A Bias-Variance Decomposition of Information Transfer in Multi-Task Learning

### 2020-08-17 arxiv/setup.tex
sec 2 wip

Following \citet{HMRT19} and \citet{BLLT20},
%In the high-dimensional linear regression setting (e.g. ), the features of the $k$-th task, denoted by $X_k\in\real^{n_i\times p}$, consist of $n_k$ feature vectors given by $x_1, x_2, \dots, x_{n_k}$.
we assume that for each task $k$ from $1$ to $t$, each feature vector $x_i = \Sigma^{1/2}_k z_i$, where $z_i\in\real^p$ consists of i.i.d. entries with mean zero and unit variance.
The sample size of task $k$, given by $n_k$, is equal to $\rho_k\cdot p$ for a fixed value $\rho_k$.
This setting is also known as the high-dimensional linear regression setting in the literature.
%The labels $Y_k = X_k \beta_k + \varepsilon_k$, where $\beta_k$ denotes the linear model parameters and $\varepsilon_k$ denotes i.i.d. noise with mean zero and variance $\sigma^2$.
%Recall that we have $t$ labeled training datasets, denoted by $(X_1, Y_1), (X_2, Y_2), \dots, (X_t, Y_t)$, where $X_i\in\real^{n_i\times p}$ and $Y_i\in\real^{n_i}$ for $1\le i\le t$.
%Following \cite{HMRT19,BLLT20}, we assume that for each task $i = 1,2,\dots,t$,  every feature vector is generated as $x = \Sigma_i^{1/2} z$, where $z\in\real^p$ is a random vector with i.i.d. entries of mean zero and unit variance and $\Sigma_i\in\real^{p\times p}$ is a positive semidefinite matrix.
%Without loss of generality, let the $t$-th task be the target task.

>>>>

Following \citet{HMRT19} and \citet{BLLT20},
%In the high-dimensional linear regression setting (e.g. ), the features of the $k$-th task, denoted by $X_k\in\real^{n_i\times p}$, consist of $n_k$ feature vectors given by $x_1, x_2, \dots, x_{n_k}$.
we assume that for each task $k$ from $1$ to $t$, each feature vector $x_i = \Sigma^{1/2}_k z_i$ for $i = 1, \dots, n_k$, where $z_i\in\real^p$ is an i.i.d. random vector with  mean zero and unit variance.
The sample size of task $k$, given by $n_k$, is equal to $\rho_k\cdot p$ for a fixed value $\rho_k$ that does not grow with feature dimension $p$.
This setting is also known as the high-dimensional linear regression setting in the literature.
There are two motivations for studying the high-dimensional linear regression setting for multi-task learning.
First, this setting captures salient properties of modern large-scale datasets, where the sample sizes are usually on the order of tens to hundreds of the number of features \cite{sur2019modern}.
Second, as we will see soon in Section \ref{sec_main}, we can derive precise asymptotics of the generalization error that scale with properties of the task data such as sample sizes.
%The labels $Y_k = X_k \beta_k + \varepsilon_k$, where $\beta_k$ denotes the linear model parameters and $\varepsilon_k$ denotes i.i.d. noise with mean zero and variance $\sigma^2$.
%Recall that we have $t$ labeled training datasets, denoted by $(X_1, Y_1), (X_2, Y_2), \dots, (X_t, Y_t)$, where $X_i\in\real^{n_i\times p}$ and $Y_i\in\real^{n_i}$ for $1\le i\le t$.
%Following \cite{HMRT19,BLLT20}, we assume that for each task $i = 1,2,\dots,t$,  every feature vector is generated as $x = \Sigma_i^{1/2} z$, where $z\in\real^p$ is a random vector with i.i.d. entries of mean zero and unit variance and $\Sigma_i\in\real^{p\times p}$ is a positive semidefinite matrix.
%Without loss of generality, let the $t$-th task be the target task.
